V4 Neural Network Model for Shape-based Feature Extraction and Object Discrimination

### 2015-09-10 article.tex
fix image path in latex

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{subfig}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{setspace}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.8\linewidth]{images/fig1.jpg}} 
\caption{V4 is an intermediate stage in visual recognition.}
\label{fig:1}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[]{\includegraphics[width=0.18\linewidth]{images/fig2a.jpg}\label{fig:2a}}\hfil
\subfloat[]{\includegraphics[width=0.36\linewidth]{images/fig2b.jpg}\label{fig:2b}}\hfil
\subfloat[]{\includegraphics[width=0.36\linewidth]{images/fig2c.jpg}\label{fig:2c}}
\caption{Shapes to examine V4 selectivity.
(a) Sinusoidal gratings. (b) Non-Cartesian gratings. (c) Closed shapes.}
\label{fig:2}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=\linewidth]{images/fig3.eps}} 
\caption{Multilayer neural network model of V4.}
\label{fig:3}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.8\linewidth]{images/fig4.jpg}} 
\caption{Entropy of image patches.
Bar charts in the second row show the output values of complex cells
with different preferred orientations (from $0^\circ$ to $180^\circ$).}
\label{fig:4}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[Car image]{\includegraphics[width=0.32\linewidth]{images/fig5a.jpg}\label{fig:5a}}\hfil
\subfloat[Activity map]{\includegraphics[width=0.32\linewidth]{images/fig5c.jpg}\label{fig:5b}}\hfil
\subfloat[Entropy map]{\includegraphics[width=0.32\linewidth]{images/fig5e.jpg}\label{fig:5c}}\\
\subfloat[Face image]{\includegraphics[width=0.32\linewidth]{images/fig5b.jpg}\label{fig:5d}}\hfil
\subfloat[Activity map]{\includegraphics[width=0.32\linewidth]{images/fig5d.jpg}\label{fig:5e}}\hfil
\subfloat[Entropy map]{\includegraphics[width=0.32\linewidth]{images/fig5f.jpg}\label{fig:5f}}\\
\subfloat[Salient points]{\includegraphics[width=0.49\linewidth]{images/fig5g.jpg}\label{fig:5g}}\hfil
\subfloat[Salient points]{\includegraphics[width=0.49\linewidth]{images/fig5h.jpg}\label{fig:5h}}
\caption{Detecting salient points. (a)(d) Original images.
(b)(e) Complex cell activity map. 
(c)(f) Entropy map.
In the maps, red color indicates high value and blue color indicates low value.
(g)(h) Salient points at the scale of 4, 8, and 16 in terms of simple cell radius.}
\label{fig:5}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.99\linewidth]{images/fig6.eps}} 
\caption{RBM encoder for local shape feature.}
\label{fig:6}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[Response map]{\includegraphics[width=0.48\linewidth]{images/fig7a.jpg}\label{fig:7a}}\hfil
\subfloat[Weight matrices]{\includegraphics[width=0.48\linewidth]{images/fig7b.jpg}\label{fig:7b}}
\caption{Response map and weight matrices of a perceptron that distinguishes two shapes.
(a) The perceptron prefers the shape in the left half of the samples.
It is insensitive to small changes in the position of the shape.
(b) The input weight of the perceptron. 
Each block shows the weight of connections from complex cells of a certain orientation.
Complex cells of 18 different orientations provide input for this perceptron.}
\label{fig:7}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[]{\includegraphics[width=0.24\linewidth]{images/fig8a.jpg}\label{fig:8a}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{images/fig8b.jpg}\label{fig:8b}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{images/fig8c.jpg}\label{fig:8c}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{images/fig8d.jpg}\label{fig:8d}}
\caption{RBM output units responding to convex curves towards certain directions.
(a) Sample patterns of segmented curves.
(b-d) Selectivity indexes and response maps of units tuned for upward, downward, and top-left projections. }
\label{fig:8}
\end{figure}

\begin{figure}[!t]
\centering
\subfloat[Response map of a unit selective for a pair of circular sectors (selectivity index = 3.92).]%
{\includegraphics[width=0.9\linewidth]{images/fig9a.jpg}\label{fig:9a}}\\
\subfloat[Response map of a unit selective for helix shapes (Selectivity index = 6.37).]%
{\includegraphics[width=0.9\linewidth]{images/fig9b.jpg}\label{fig:9b}}
\caption{Response maps of RBM units tuned for non-Cartesian gratings.}
\label{fig:9}
\end{figure}

\begin{figure}[!t]
\centering
\subfloat[Patterns]{\includegraphics[width=0.31\linewidth]{images/fig10a.jpg}\label{fig:10a}}\hfil
\subfloat[Response map]{\includegraphics[width=0.31\linewidth]{images/fig10b.jpg}\label{fig:10b}}\hfil
\subfloat[Response map]{\includegraphics[width=0.31\linewidth]{images/fig10c.jpg}\label{fig:10c}}
\caption{RBM units responding to closed shapes.}
\label{fig:10}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Matching between the same face]{
    \includegraphics[width=0.8\linewidth]{images/fig11a.jpg}
    \label{fig:11a}}\\
  \subfloat[Matching between different faces]{
    \includegraphics[width=0.8\linewidth]{images/fig11b.jpg}
    \label{fig:11b}}
\caption{Matching face images.}
\label{fig:11}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Our match]{
    \includegraphics[width=0.8\linewidth]{images/fig12a.jpg}
    \label{fig:12a}}\\
  \subfloat[SIFT match]{
    \includegraphics[width=0.8\linewidth]{images/fig12b.jpg}
    \label{fig:12b}}
\caption{Comparison of feature matching between van images.}
\label{fig:12}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.9\linewidth]{images/fig13.eps}} 
\caption{Matching facial features in Caltech-101 ``Face-easy'' category.}
\label{fig:13}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Sampling density of orientations]{
    \includegraphics[width=0.9\linewidth]{images/fig14a.eps}
    \label{fig:14a}}\\
  \subfloat[Number of features per image]{
    \includegraphics[width=0.9\linewidth]{images/fig14b.eps}
    \label{fig:14b}}
\caption{Performance with different parameters.}
\label{fig:14}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Comparison with other methods]{
    \includegraphics[width=0.9\linewidth]{images/fig15a.eps}
    \label{fig:15a}}\\
  \subfloat[Comparison with other features]{
    \includegraphics[width=0.9\linewidth]{images/fig15b.eps}
    \label{fig:15b}}
\caption{Comparison of performance.}
\label{fig:15}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{subfig}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.8\linewidth]{fig1.jpg}} 
\caption{V4 is an intermediate stage in visual recognition.}
\label{fig:1}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[]{\includegraphics[width=0.18\linewidth]{fig2a.jpg}\label{fig:2a}}\hfil
\subfloat[]{\includegraphics[width=0.36\linewidth]{fig2b.jpg}\label{fig:2b}}\hfil
\subfloat[]{\includegraphics[width=0.36\linewidth]{fig2c.jpg}\label{fig:2c}}
\caption{Shapes to examine V4 selectivity.
(a) Sinusoidal gratings. (b) Non-Cartesian gratings. (c) Closed shapes.}
\label{fig:2}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=\linewidth]{fig3.eps}} 
\caption{Multilayer neural network model of V4.}
\label{fig:3}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.8\linewidth]{fig4.jpg}} 
\caption{Entropy of image patches.
Bar charts in the second row show the output values of complex cells
with different preferred orientations (from $0^\circ$ to $180^\circ$).}
\label{fig:4}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[Car image]{\includegraphics[width=0.32\linewidth]{fig5a.jpg}\label{fig:5a}}\hfil
\subfloat[Activity map]{\includegraphics[width=0.32\linewidth]{fig5c.jpg}\label{fig:5b}}\hfil
\subfloat[Entropy map]{\includegraphics[width=0.32\linewidth]{fig5e.jpg}\label{fig:5c}}\\
\subfloat[Face image]{\includegraphics[width=0.32\linewidth]{fig5b.jpg}\label{fig:5d}}\hfil
\subfloat[Activity map]{\includegraphics[width=0.32\linewidth]{fig5d.jpg}\label{fig:5e}}\hfil
\subfloat[Entropy map]{\includegraphics[width=0.32\linewidth]{fig5f.jpg}\label{fig:5f}}\\
\subfloat[Salient points]{\includegraphics[width=0.49\linewidth]{fig5g.jpg}\label{fig:5g}}\hfil
\subfloat[Salient points]{\includegraphics[width=0.49\linewidth]{fig5h.jpg}\label{fig:5h}}
\caption{Detecting salient points. (a)(d) Original images.
(b)(e) Complex cell activity map. 
(c)(f) Entropy map.
In the maps, red color indicates high value and blue color indicates low value.
(g)(h) Salient points at the scale of 4, 8, and 16 in terms of simple cell radius.}
\label{fig:5}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.99\linewidth]{fig6.eps}} 
\caption{RBM encoder for local shape feature.}
\label{fig:6}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[Response map]{\includegraphics[width=0.48\linewidth]{fig7a.jpg}\label{fig:7a}}\hfil
\subfloat[Weight matrices]{\includegraphics[width=0.48\linewidth]{fig7b.jpg}\label{fig:7b}}
\caption{Response map and weight matrices of a perceptron that distinguishes two shapes.
(a) The perceptron prefers the shape in the left half of the samples.
It is insensitive to small changes in the position of the shape.
(b) The input weight of the perceptron. 
Each block shows the weight of connections from complex cells of a certain orientation.
Complex cells of 18 different orientations provide input for this perceptron.}
\label{fig:7}
\end{figure}

@@

\begin{figure}[!t]
\centering
\subfloat[]{\includegraphics[width=0.24\linewidth]{fig8a.jpg}\label{fig:8a}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{fig8b.jpg}\label{fig:8b}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{fig8c.jpg}\label{fig:8c}}\hfil
\subfloat[]{\includegraphics[width=0.24\linewidth]{fig8d.jpg}\label{fig:8d}}
\caption{RBM output units responding to convex curves towards certain directions.
(a) Sample patterns of segmented curves.
(b-d) Selectivity indexes and response maps of units tuned for upward, downward, and top-left projections. }
\label{fig:8}
\end{figure}

\begin{figure}[!t]
\centering
\subfloat[Response map of a unit selective for a pair of circular sectors (selectivity index = 3.92).]%
{\includegraphics[width=0.9\linewidth]{fig9a.jpg}\label{fig:9a}}\\
\subfloat[Response map of a unit selective for helix shapes (Selectivity index = 6.37).]%
{\includegraphics[width=0.9\linewidth]{fig9b.jpg}\label{fig:9b}}
\caption{Response maps of RBM units tuned for non-Cartesian gratings.}
\label{fig:9}
\end{figure}

\begin{figure}[!t]
\centering
\subfloat[Patterns]{\includegraphics[width=0.31\linewidth]{fig10a.jpg}\label{fig:10a}}\hfil
\subfloat[Response map]{\includegraphics[width=0.31\linewidth]{fig10b.jpg}\label{fig:10b}}\hfil
\subfloat[Response map]{\includegraphics[width=0.31\linewidth]{fig10c.jpg}\label{fig:10c}}
\caption{RBM units responding to closed shapes.}
\label{fig:10}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Matching between the same face]{
    \includegraphics[width=0.8\linewidth]{fig11a.jpg}
    \label{fig:11a}}\\
  \subfloat[Matching between different faces]{
    \includegraphics[width=0.8\linewidth]{fig11b.jpg}
    \label{fig:11b}}
\caption{Matching face images.}
\label{fig:11}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Our match]{
    \includegraphics[width=0.8\linewidth]{fig12a.jpg}
    \label{fig:12a}}\\
  \subfloat[SIFT match]{
    \includegraphics[width=0.8\linewidth]{fig12b.jpg}
    \label{fig:12b}}
\caption{Comparison of feature matching between van images.}
\label{fig:12}
\end{figure}

@@

\begin{figure}[!t]
\centerline{\includegraphics[width=0.9\linewidth]{fig13.eps}} 
\caption{Matching facial features in Caltech-101 ``Face-easy'' category.}
\label{fig:13}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Sampling density of orientations]{
    \includegraphics[width=0.9\linewidth]{fig14a.eps}
    \label{fig:14a}}\\
  \subfloat[Number of features per image]{
    \includegraphics[width=0.9\linewidth]{fig14b.eps}
    \label{fig:14b}}
\caption{Performance with different parameters.}
\label{fig:14}
\end{figure}

@@

\begin{figure}[!t]
\centering
  \subfloat[Comparison with other methods]{
    \includegraphics[width=0.9\linewidth]{fig15a.eps}
    \label{fig:15a}}\\
  \subfloat[Comparison with other features]{
    \includegraphics[width=0.9\linewidth]{fig15b.eps}
    \label{fig:15b}}
\caption{Comparison of performance.}
\label{fig:15}
\end{figure}
